\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-09-27 challenge.tex
Challenge#4

\noindentparagraph{Family vs.\ interactivity.}

>>>>

\noindentparagraph{User experience.}

Interactive theorem proving and tactic programming are
part of the idiomatic programming experience in a proof assistant.
A language design integrating family polymorphism should be compatible
with these programming styles.
For instance, it should be possible in our tool to
incrementally navigate through vernacular commands and construct proofs
using tactics with instant feedback on the proof state,
even in the middle of a family definition.
